% !TeX spellcheck = en_GB
% !TeX program = pdflatex
%
% LuxSleek-CV 1.1 LaTeX template
% Author: Andreï V. Kostyrka, University of Luxembourg
%
% 1.1: added tracking and letter-spacing for prettier lower caps, added `~` for language levels
% 1.0: initial release

\documentclass[11pt, a4paper]{article} 

\usepackage[T1]{fontenc}     % We are using pdfLaTeX,
\usepackage[utf8]{inputenc}  % hence this preparation
\usepackage[british]{babel}  
\usepackage[left = 0mm, right = 0mm, top = 0mm, bottom = 0mm]{geometry}
\usepackage[stretch = 25, shrink = 25, tracking=true, letterspace=30]{microtype}  
\usepackage{graphicx}        % To insert pictures
\usepackage{xcolor}          % To add colour to the document
\usepackage{marvosym}        % Provides icons for the contact details

\usepackage{enumitem}        % To redefine spacing in lists
\setlist{parsep = 0pt, topsep = 0pt, partopsep = 1pt, itemsep = 1pt, leftmargin = 6mm}

\usepackage{FiraSans}        % Change this to use any font, but keep it simple
\usepackage{fontawesome5}

\renewcommand{\familydefault}{\sfdefault}

\definecolor{cvblue}{HTML}{304263}

%%%%%%% USER COMMAND DEFINITIONS %%%%%%%%%%%%%%%%%%%%%%%%%%%
% These are the real workhorses of this template
\newcommand{\dates}[1]{\hfill\mbox{\textbf{#1}}} % Bold stuff that doesn’t got broken into lines
\newcommand{\is}{\par\vskip.5ex plus .4ex} % Item spacing
\newcommand{\smaller}[1]{{\small$\diamond$\ #1}}
\newcommand{\headleft}[1]{\vspace*{3ex}\textsc{\textbf{#1}}\par%
    \vspace*{-1.5ex}\hrulefill\par\vspace*{0.7ex}}
\newcommand{\headright}[1]{\vspace*{2.5ex}\textsc{\Large\color{cvblue}#1}\par%
     \vspace*{-2ex}{\color{cvblue}\hrulefill}\par}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\usepackage[colorlinks = true, urlcolor = white, linkcolor = white]{hyperref}

\begin{document}

% Style definitions -- killing the unnecessary space and adding the skips explicitly
\setlength{\topskip}{0pt}
\setlength{\parindent}{0pt}
\setlength{\parskip}{0pt}
\setlength{\fboxsep}{0pt}
\pagestyle{empty}
\raggedbottom

\begin{minipage}[t]{0.33\textwidth} %% Left column -- outer definition
%  Left column -- top dark rectangle

% \vspace{-.2ex} % Eliminates the small gap
\colorbox{cvblue!90}{\color{white}  %% LEFT BOX
\kern0.09\textwidth\relax% Left margin provided explicitly
\begin{minipage}[t][297mm][t]{0.82\textwidth}
\raggedright
\vspace*{4.5ex}

\LARGE Federico Gratti \normalsize 

{\small Full Stack Developer}

\vspace*{0.5ex} % Extra space after the picture

\headleft{Info}
\small % To fit more content
\makebox[1em][c]{\faIcon{birthday-cake}}\hspace{0.4em}{\small 20 September 1990} \\[0.4ex]
\makebox[1em][c]{\faIcon{map-marker-alt}}\hspace{0.4em}\href{https://maps.app.goo.gl/cADAfNeVxmCRT9Km8}{La Plata, Argentina} \\[0.5ex]
\makebox[1em][c]{\faIcon{github}}\hspace{0.4em}\href{https://github.com/fedegratti}{github.com/fedegratti} \\[0.5ex]
\makebox[1em][c]{\faIcon{envelope}}\hspace{0.4em}\href{mailto:federicogratti@gmail.com}{federicogratti@gmail.com} \\[0.4ex]
% \makebox[1em][c]{\faIcon{mobile-alt}}\hspace{0.4em}+54\,9\,221\,547\,8491 \\[0.5ex] 
\normalsize

\headleft{About me}
Technology has always been more than a job for me.

I actively build applications in my free time and explore new tools out of curiosity. I'm a proactive and reliable engineer with strong communication skills, driven by continuous learning and meaningful problem-solving.

\headleft{Career Goals}
I’m looking to join a company that values continuous professional and personal growth. I'm motivated by being part of collaborative teams that embrace new technologies and encourage constant learning.

% \headleft{Personal information}
% %Year of birth: \textbf{1861} \\[0.5ex]
% Citizenship: \textbf{Argentina} \\[0.5ex]
% Family: \textbf{Married without children} \\[0.5ex]
% Languages: \textbf{English}~(B2), \textbf{Spanish}~(native)

% \headleft{Skills}
% \begin{itemize}
% \item Ruby, Javascript, Typescript
% \item Ruby on Rails, SQL, React.js
% \item Three.js, Pug.js, SASS, HTML5, CSS3
% \item Communication and team collaboration
% \end{itemize} 

\end{minipage}%
\kern0.09\textwidth\relax%%Right margin provided explicitly to stretch the colourbox
}
\end{minipage}% Right column
\hskip2.3em% Left margin for the white area
\begin{minipage}[t]{0.58\textwidth}
\setlength{\parskip}{0.8ex}% Adds spaces between paragraphs; use \\ to add new lines without this space. Shrink this amount to fit more data vertically

\vspace{2ex}

\headright{Experience}

\textsc{Senior Full Stack Developer} at \textit{OHZI Interactive}  \dates{2021.12--present} \\
\smaller{Designed and maintained production-ready Ruby on Rails APIs.} \\
\smaller{Involved in robust interactive frontend development.} \\
\smaller{Built automation tools that improved development workflows and efficiency.} \\
\smaller{Implemented real-time communication between backend and frontend.} \\
\smaller{Led dailies with clients, aligning technical execution with business needs.}

{\small\textsc{Skills}: Ruby, JavaScript, TypeScript, Ruby on Rails, React.js, PostgreSQL, AWS.}

\is
\is
\textsc{Senior Front End Developer} at \textit{OHZI Interactive}  \dates{2019.01--2021.12} \\
\smaller{Built an in-house JS framework focused on performant 3D web experiences.} \\
\smaller{Implemented interactive 3D applications using modern frontend technologies.} \\
\smaller{Partnered with designers to deliver intuitive user experiences.}

{\small\textsc{Skills}: JavaScript, TypeScript, REST APIs, Three.js, Git, Node.js, WebSocket.}

\is
\is
\textsc{Full Stack Developer} at \textit{Weblinc Commerce} \dates{2016.03--2019.02} \\
\smaller{Delivered 10+ e-commerce solutions using an internal framework.} \\
\smaller{Built custom applications tailored to specific Shopify store requirements.} \\
\smaller{Contributed to a fully remote Scrum team, collaborating across time zones.}

{\small\textsc{Skills}: Ruby, JavaScript, Ruby on Rails, MongoDB, Redis.}

\is
\is
\textsc{Java SSR Developer} at \textit{Fluxit}  \dates{2015.03--2016.03} \\
\smaller{Developed backend systems to manage complex internal client workflows.} \\
\smaller{Applied Scrum practices to ensure predictable and efficient delivery.} \\
\smaller{Contributed to the design and implementation of robust software solution.}

{\small\textsc{Skills}: Java, Spring, Scrum, SQL Server, Git, Agile methodologies.}

\is
\is
\textsc{Game Developer} at \textit{Teardrop}  \dates{2014.01--2015.12} \\
\smaller{Designed and developed Touch the Circle using C\# and Unity3D.} \\
\smaller{Implemented core gameplay mechanics, including tap-and-hold movement.} \\
\smaller{Co-developed Foxy Fox, handling gameplay logic and asset integration.} \\
\smaller{Applied OOP principles such as inheritance, polymorphism, and abstraction.} 

{\small\textsc{Skills}: C\#, Unity3D, Git, Agile methodologies.}

\is
\headright{Education}

\textsc{Computer Science}. \textit{Universidad Nacional de La Plata}. \dates{2011--2018}

\is
\textsc{Programmer Analyst}. \textit{Universidad Nacional de La Plata}. \dates{2011--2017}

% \headright{Hobbies}

% \textsc{Sing:} In my free time I go to a sing academy and perform 2 live shows per year.

% \textsc{More programming:} I love programming in my free time, building small apps and exploring new technologies.

% \textsc{Traveling:} I love to travel and explore new cultures and cuisines.

% \textsc{Miscelxlaneous:} Movies, Broadway shows.

\end{minipage}
\end{document}